The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-28 manuscript.Rmd
[fix #29] plot proportions of lot identified at species level

>>>>

## Supplementary material

```{r id_though_time, fig.cap='Proportion of specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected identified at the species level suggesting a lack of expertise to identify precisely what is collected.'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```
